What is happening on Twitter? A framework for student research projects with tweets

### 2020-06-01 Rmd/jse-special-issue-2020.Rmd
updated manuscript with summ assessments table.

In future iterations, we will use a written rubric to grade student theses. We'll
share the rubric with our students at the start of the academic year.

>>>>

```{r, summative, echo = FALSE, fig.cap = "Rubric for summative assessment of learning objectives."}
summative <- readr::read_csv("../data/summative-assessments.csv")
knitr::kable(summative, caption = "Rubric for summative assessment of learning objectives.")
```

In future iterations, we will use a written rubric to grade student theses (Table \@ref(tab:summative) ). We'll
share the rubric with our students at the start of the academic year.
